Supplements for the manuscript `Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO-CC'

### 2024-09-23 supplements/supplements.Rmd
revisions 1

>>>>

```{r}
data <- read_csv("../data/data.csv") %>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe",
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)",
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)",
                            uganda = "Nyabyeya (Uganda)"),
      imprecision = abs(clickdistfromtargetcenterx)/160,
      centrality = as.character(abs(5-targetposition)), 
      age_group = floor(ageinyears)) %>% 
  filter(trialtype == "test", voiceover == F) %>%
  mutate(trialnr = as.numeric(factor(trialnr))) 
```

# Participants

```{r demtable, echo=F}
demtab <- data %>%
  separate(community, into = c("community", "country"), sep = " \\(")%>%
  mutate(country = str_remove(country, "\\("),
         country = str_remove(country, "\\)"))%>%
  distinct(subjid, .keep_all = T)%>%
  group_by(community, country, continent)%>%
  summarise(N = n_distinct(subjid), 
            mean_age = mean(ageinyears),
            min_age = min(ageinyears), 
            max_age = max(ageinyears))%>%
  mutate_if(is.numeric, format, digits = 2, nsmall = 2)%>%
  mutate(age = mean_age, 
         range = paste(min_age, " - ", max_age)) %>%
  select(-c(mean_age, min_age, max_age))%>%
  arrange(community)

kableExtra::kable(demtab,
             col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
              caption = "Participant demographics.", 
             format="latex", booktabs=TRUE
             )
```

### 2024-09-23 supplements/supplements.tex
revisions 1

>>>>

\section{Participants}\label{participants}

\begin{table}

\caption{\label{tab:demtable}Participant demographics.}
\centering
\begin{tabular}[t]{llllll}
\toprule
Community & Country & Continent & N & Sex (male) & Age (range)\\
\midrule
Akure & Nigeria & Africa & 114 & 5.07 & 2.57  -  7.33\\
Auckland & New Zealand & Oceania & 43 & 5.14 & 2.81  -  8.75\\
BaYaka & Rep. Congo & Africa & 29 & 7.80 & 3.94  -  10.56\\
Bandongo & Rep. Congo & Africa & 30 & 7.45 & 3.50  -  10.95\\
Beijing & China & Asia & 123 & 5.47 & 2.69  -  8.48\\
\addlinespace
Buenos Aires & Argentina & Americas & 105 & 4.72 & 3.00  -  6.96\\
Chimfunshi & Zambia & Africa & 22 & 5.98 & 2.88  -  8.00\\
Hai||om & Namibia & Africa & 60 & 5.85 & 2.74  -  8.34\\
Khwe & Namibia & Africa & 59 & 5.84 & 3.38  -  8.63\\
Leipzig & Germany & Europe & 100 & 4.88 & 2.53  -  6.95\\
\addlinespace
Malatya & Türkiye & Asia & 85 & 5.02 & 2.75  -  7.12\\
Nyabyeya & Uganda & Africa & 125 & 5.94 & 2.67  -  8.92\\
Ocuilan & Mexico & Americas & 127 & 4.96 & 2.57  -  6.95\\
Plymouth & UK & Europe & 70 & 6.02 & 2.38  -  8.94\\
Pune & India & Asia & 148 & 6.14 & 3.06  -  8.83\\
\addlinespace
Stanford & USA & Americas & 98 & 4.99 & 2.52  -  7.90\\
Windhoek & Namibia & Africa & 39 & 5.69 & 2.66  -  8.66\\
\bottomrule
\end{tabular}
\end{table}
